---
title: "1013R-basics-Markdown"
output: html_document
---

# Assignment and Variable names
```{r}
a = log2(32)

```

# data type
```{r cars}
rm(list=ls())
typeof(1+0i)
a = c(1L,1.5)
typeof(c(list(1)))
typeof(list(c(1,2)))
x <- list(1:3, "a", c(TRUE, FALSE, TRUE), c(2.3, 5.9))
x
c(list(1,2),list(3,4))
list(list(1,2),list(3))

x=c(1,2,3)
class(x)
class(factor(x))
a=1:6
dim(a)=c(3,2)
a
matrix( 1 : 6 , ncol=2, nrow=3)  

x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')

x[c(1,1,3)]
which(names(x)=="b")
x[x > 10]

```

# data structure
```{r cars}
df  <-	data.frame(  x = 1:3, 
                     y = c ( " a " ,  " b " ,	" c " ) ,
                     stringsAsFactors  = FALSE)
df 
typeof(df$x)
# subsetting  the  first	row  df[1,] 
# subsetting rows where df$x>1
df[ df$x> 1 , ]

```
```


```{r cars}


### plot
```{r}
x <- seq(-pi,pi,0.1)

plot(x, sin(x))
plot(x,x)
a = c(1,2,3)
typeof(a)
# numeric
b = c(1L,2L,3L)
typeof(b)
c = c("A","b")
typeof(c)
d = c(a,c)
typeof(d)
c(FALSE,5,6,7)
c("A",5)
```

### Compare the results of list() and c()
```{r}
x <- list(
  list(1, 2), 
  c(3, 4))
x
y <- c(list(1, 2), c(3, 4))
y
str(y)
cat("------\n")
y
typeof(x)
typeof(y)
class(x)
class(y)
```

### name
```{r}
a = c(1,2,3)
a
names(a) = paste0("n",1:2)

a[1] = 10
a

f = factor(c("a","b","b"))
f
levels(f)

f[1] = "c"

f
```

### factors
```{r}
x <- factor(c("a", "b", "b", "a"))
x
x[2] <- "c"
class(x)
as.integer(x)
b = as.character(x)
b[2] <- "c"
b
class(b)

```

###　Matrices and Arrays
```{r}
# Two scalar arguments to specify rows and columns
a <- matrix(1:6, ncol = 3, nrow = 2)
a

dim(a)

# One vector argument to describe all dimensions
b <- array(1:12, c(2, 3, 3))
b
?array
# You can also modify an object in place by setting dim()
c <- 1:6
dim(c) <- c(3, 2)
c

rownames(a) <- c("A", "B")
colnames(a) <- c("a", "b", "c")
a
```

### Subsetting
```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
x


# We can ask for multiple elements at once:
x[c(1, 3)]

# Or slices of the vector:
x[1:4]

# If we ask for a number outside of the vector, R will return missing values
x[6]

# If we ask for the 0th element, we get an empty vector:
x[0]

```
**In many programming languages (C and python, for example), the first element of a vector has an index of 0. In R, the first element is 1.**

### Skipping and removing elements
```{r}
x[-2]
x[c(-1, -5)]  # or x[-c(1,5)]

#x[-1:3] #This gives a somewhat cryptic error:
x[-(1:3)]
```

### Subsetting by name
```{r}
x
x[c("a", "c")]

# how about un-unique names?
names(x)[2] = "a"
x
x[c("a", "c")]


x[which(names(x) == "a")]
```

### Subsetting through other logical operations
```{r}
x
x[c(TRUE, TRUE, FALSE, FALSE)]
```
#### matrix 
```{r}
a = matrix(1:12,ncol=3)
a[,2]
b = matrix(1:12,ncol=4)
b
dim(a)
dim(b)
a %*% b



```


### data frame
```{r}
cats <- data.frame(coat = c("calico", "black", "tabby"), weight = c(2.1, 5.0, 3.2), likes_string = c(1, 0, 1),stringsAsFactors = FALSE)

str(cats)
cats
typeof(cats)
class(cats)
is.data.frame(cats)
cats
cats$coat
cats[1,]
```

### data I/O
```{r}
getwd()

df = read.table("../data/1014_dat.txt")
head(df,2)

class(df)
dim(df)

df

head(df,2)
df$c1  # pulling out columns by specifying them using the $ operator
df[1,]  #  subset the first row  
df$c1 > 1 # subsetting rows where df$x>1
df2 = df[df$c1 > 1,]
df2

df2$index = seq(1,7)
df2
# Adding columns and rows
nl = seq(1,5)
df3 = rbind(nl,df2)
df3


rownames(df3)[1] = "new"
df3

saveRDS(df3,"../results/res.rds")

write.table(df3,"../results/res.txt",sep="\t",quote = F)
?write.table
```

### write your own function
```{r}
a = c(NA,1,2,3,4,5)
mean(a)

meanRemoveNA <- function(x){ 
  mean(x, na.rm=TRUE) 
  }


mean(a)
meanRemoveNA(a)
```

### apply family
```{r}
cats

l = lapply(cats[,-1],meanRemoveNA)
s = sapply(cats[,-1],meanRemoveNA)
l
s
typeof(l)
typeof(s)

li <- list("klaus","martin","georg")  
lapply(li, toupper)


fct <- function(x) { return(c(x, x^2, x^3)) }
s2 = lapply(1:5, fct)
s2
class(s2)

do.call(rbind,s2)


x <- matrix(1:12, nrow=4, ncol=3)
x
apply(x, 1, sum)
apply(x, 2, mean)
paste("a","b")


```

### R packages
```{r}
.libPaths()
install.packages("data.table")


library(data.table)


f = fread("../data/Dataset_S1.txt",data.table=F)

dim(f)

head(f,2)

colnames(f)[4] = "total_Bases"
hist(f$total_Bases)

install.packages("ggplot2")

# Or the development version from GitHub:
install.packages("devtools")
devtools::install_github("tidyverse/ggplot2")
```


```{r}
f = read.csv("../data/tss_test.txt",sep="\t",header=F,stringsAsFactors=F)
f
```



